Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{{DISTRIBUTION STATEMENT A. Approved for public release.} }

### 2021-05-14 paper/case-study.tex

In total, eight cyber requirements are generated and imported into our model.  These include one \textit{sandboxing} requirement, four \textit{well-formedness} requirements, two requirements for \textit{monitoring} the behavior of the open-source UxAS component, and an \textit{attestation} requirement for ensuring the Ground Station software has not been tampered with.  Requirements are imported into the model as goals in a Resolute assurance case.  Because we can run Resolute at any time during development, we can easily determine for a given snapshot of the model which requirements are not yet supported by evidence.

@@

The AGREE filter policies for the four UxAS connections are similar, and check that record values contained in the messages are within appropriate ranges.  For example, the Automation Response message filter, which drops message containing malformed flight plans, is defined as shown in Figure~\ref{fig:automation-response-filter}.  Although Latitude, Longitude and Altitude are defined as 64-bit \textit{reals}, the filter ensures only messages containing waypoint values between (-90,90), (-180,180), and (0,15000), respectively.

@@

Once we have determined that the model is correct and satisfies its cyber requirements, and the software components in the model have been implemented, either by SPLAT or other means, the system can be built and deployed.  We run the HAMR tool to generate the component stubs and infrastructure code necessary to enable component communication and execution according to a specified schedule.
HAMR translates the AADL system model to code that implements threading infrastructure and inter-component communication and is consistent with the AADL specification computational model.
%
HAMR then compiles the software to execute on seL4~\cite{DBLP:journals/cacm/KleinAEHCDEEKNSTW10}, a
verified capability-based microkernel (accompanied by formal proof of
spatial isolation properties down to the binary level).

@@

\paragraph{UxAS vulnerability exploit} In this scenario, Line Search Tasks with greater than 90 waypoints will trigger a vulnerability that will crash UxAS.   When this occurs, UxAS be prevented from generating an Automation Response.  This vulnerability is mitigated by inserting a Response Monitor, which checks to see that UxAS outputs an Automation Response message shortly after receiving an Automation Request.  For this scenario, we chose for the monitor to output a status message, which would then be received by the ground station and an appropriate action taken.

@@

We repeated the tests on the hardened system and were able to demonstrate that our mitigations were successful, as shown in the status messages sent from the high-assurance components in Figure~\ref{fig:mitigation-output}.

\begin{figure}[h]
	\centering
	\includegraphics[width=1\columnwidth]{figs/mitigation-output.png}
	\caption{Cyber-resilient system response.} 
	\label{fig:mitigation-output} 
\end{figure}

>>>>

In total, seven cyber requirements are generated and imported into our model.  These include four \textit{well-formedness} requirements, two requirements for \textit{monitoring} the behavior of the open-source UxAS component, and an \textit{attestation} requirement for ensuring the Ground Station software has not been tampered with.  Requirements are imported into the model as goals in a Resolute assurance case.  Because we can run Resolute at any time during development, we can easily determine for a given snapshot of the model which requirements are not yet supported by evidence.

@@

The AGREE filter policies for the four UxAS connections are similar, and check that record values contained in the messages are within appropriate ranges.  For example, the Automation Response message filter, which drops message containing malformed flight plans, is defined as shown in Figure~\ref{fig:automation-response-filter}.  Although Latitude, Longitude and Altitude are defined as 64-bit \textit{reals}, the filter ensures only messages containing waypoint values between [-90,9], [-180,180], and [0,15000], respectively.

@@

Once we have determined that the model is correct and satisfies its cyber requirements, and the software components in the model have been implemented, either by SPLAT or other means, the system can be built and deployed.  We run the HAMR tool to generate the component stubs and infrastructure code necessary to enable component communication and execution according to a specified schedule.
HAMR translates the AADL system model to code that implements threading infrastructure and inter-component communication and is consistent with the AADL specification computational model.
%
HAMR then compiles the software to execute on seL4~\cite{sel4-2009}, a verified capability-based microkernel (accompanied by formal proof of spatial isolation properties down to the binary level).

@@

\paragraph{UxAS vulnerability exploit} In this scenario, Line Search Tasks with greater than 90 waypoints will trigger a vulnerability that will crash UxAS.   When this occurs, UxAS be prevented from generating an Automation Response.  This vulnerability is mitigated by inserting a Response Monitor, which checks to see that UxAS outputs an Automation Response message shortly after receiving an Automation Request.  For this scenario, we chose for the monitor to output a status message, which would then be received by the Ground Station and an appropriate action taken.

@@

We repeated the tests on the hardened system and were able to demonstrate that our mitigations were successful, as indicated by the status messages sent from the high-assurance components, shown in Figure~\ref{fig:mitigation-output}.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.8\columnwidth]{figs/mitigation-output.png}
	\caption{Cyber-resilient system response.} 
	\label{fig:mitigation-output} 
\end{figure}
